\section{Limitations}
While our proposed multi-agent benchmark and framework provide a diverse range of tasks and evaluation metrics, several areas warrant further exploration to enhance their applicability and robustness:

\paragraph{Expanding Scenario and Model Coverage.}
Currently, our benchmark focuses on specific domains such as research co-authoring, Minecraft building, database error analysis, coding collaboration, and select competitive scenarios (e.g., Werewolf and bargaining). To better capture the complexity of real-world multi-agent interactions, future work can incorporate more diverse settings, including open-world environments, scenarios requiring richer social cognition, and tasks on the application side like task-oriented dialogues. In the aspect of models, our work does not cover the full spectrum. Future work may include the result of other latest ones (e.g. the DeepSeek model family).

\paragraph{Enhancing Ablation Studies.}
Our current analysis focuses primarily on overall coordination and competition performance, leaving finer-grained insights into specific components underexplored. Future experiments can be focused on different memory mechanisms (e.g. long-term memory, short-term memory, shared memory) and multiagent different workflow method.

\paragraph{Advancing Competition Mechanisms.}
While our benchmark incorporates competitive tasks, it does not fully capture the complexity of real-world multi-agent interactions involving multi-party negotiations, repeated strategic play, or stochastic elements. Investigating how agents transition between cooperative and adversarial roles in evolving environments remains a promising direction.

\paragraph{Handling Open-Ended and Ill-Defined Tasks.}
Most tasks in our framework involve well-defined objectives, such as completing a research proposal or resolving database inconsistencies. However, real-world applications often require agents to operate in open-ended or ambiguous contexts without clear success criteria. Future extensions could explore how multi-agent systems adapt to exploratory, non-goal-oriented scenarios.
